Community context determines competition vs. facilitation trade-offs in pollination systems

### 2019-06-17 paper/manuscript.Rmd
Use journal abbreviations in references
Explain that word count includes methods section

loadd(abs_wordcount, msc_wordcount, n_displays, n_references, keywords)
```

@@

**Type of article:** Primary research article

**Number of words:** `r abs_wordcount$n_words_stri` in abstract; `r format(round(msc_wordcount$n_words_stri), big.mark = ",")` in main text.

>>>>

loadd(abs_wordcount, msc_wordcount, n_displays, n_references, keywords, references)
```

@@

<!-- **Type of article:** Primary research article -->

**Number of words:** `r abs_wordcount$n_words_stri` in abstract; `r format(round(msc_wordcount$n_words_stri), big.mark = ",")` in main text (including Methods section).
